Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-27 paper-1/manuscript.tex
Rev F7 legend

\begin{figure*}%
    \centering
    \includegraphics{fig7.pdf}
    \caption{}
    \label{fig7}
\end{figure*}
% TODO 7: Add F6 conclusion to complete the story
% Consider alternative ways of presenting the left side without using so much space/mental effort (stats?)
% a-c: Add (dev-msc) to yaxis label
% d,e: Mark significance
\textbf{Fig. 7} Adding STD to the model enhances the direct effect of TA.
\textbf{a} Contrast (dev - msc) of the response to A, in terms of mean number of spikes per trial, in the sample network, with each neuron shown in its spatial location. Left and middle column, full model with STD and TA, and ablated model with only TA, respectively. Right column, subtraction of these two. Stimulus locations are as shown in Figure \ref{fig5}a.
\textbf{b} Contrast of mean $V_{TA}$ at the start of target trials, in columns as in panel a.
\textbf{c} Contrast of the response to non-target stimuli, in columns as in panel a.
\textbf{d} Network-wide mean contrast of the response to target (left) and non-target stimuli (right) across networks and stimuli, arranged equivalently to the columns in panels a-c. Blue and green boxes represent the full and ablated model, respectively, and white boxes the difference between these two.
\textbf{e} Network-wide mean contrast of $V_{TA}$ before A trials across networks and stimuli, arranged as in panel d

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig7.pdf}
    \caption{}
    \label{fig7}
\end{figure*}
\textbf{Fig. 7} Adding STD to the model maintains or slighly enhances the effects of TA.
\textbf{a} Median contrast (dev - msc) in the non-target response (top) and in $V_{TA}$ (bottom) among early and late neurons, respectively, across networks and stimuli, in the full model with both STD and TA. Compare to Figure \ref{fig6}c-d.
\textbf{b} Top: Median contrast (dev - msc) in the non-target response magnitude across networks and stimuli, plotted against the Pearson correlation coefficients $\rho$ of the linear correlation between non-target response contrast and $\Delta V_{TA}$ at the start of target trials across excitatory neurons. Each marker corresponds to one network and target stimulus. Data from the full model with STD and TA, compare Figure \ref{fig5}d. Middle: Non-target response contrast in the full model, plotted against the same contrast in the TA-only model. The red line is the identity function; points above this line represent networks with greater response reduction (dev - msc) in the full model than in the ablated model. Bottom: Subtraction of the two response contrasts.
\textbf{c} Top: Median contrast (dev - msc) in $V_{TA}$ at the start of target trials across networks and stimuli, plotted against the Pearson correlation coefficients $\rho$ of the linear correlation between $\Delta V_{TA}$ and the target response contrast across excitatory neurons. Each marker corresponds to one network and target stimulus. Data from the full model with STD and TA, compare Figure \ref{fig4}e. Middle: $\Delta V_{TA}$ in the full model, plotted against the same contrast in the TA-only model. The red line is the identity function; points above this line represent networks with greater reduction (dev - msc) in $V_{TA}$ in the full model than in the ablated model. Bottom: Subtraction of the two $V_{TA}$ contrasts.
